Compute last modified dates

### 2022-11-30 src/check_links.Rmd
Improved display of counts in check_links.Rmd

```{r md_links}
sim1 <- "[sim1]: http://www.pmean.com/"
full_file_name <- paste0(new_path, md_files$yr, "/", md_files$fn)
md_links <- NULL
for (i_fn in full_file_name) {
  read_lines(i_fn) %>%
    str_subset(fixed(sim1)) %>%
    str_replace(fixed(sim1), "") -> md_link
  md_link <- ifelse(length(md_link>0), md_link[1], "No link")
  md_file <- str_replace(i_fn, new_path, "")
  md_year <- str_sub(md_file, 1, 2)
  md_file <- str_sub(md_file, 4)
  md_links <- bind_rows(md_links, data.frame(md_year, md_file, md_link))
}
kable(md_links[1:10, ])
md_links %>%
  mutate(link=(md_link!="No link")) %>%
  count(md_year, link) %>%
  data.frame
```

@@

```{r html_links}
moved1 <- '<p>This page has moved to <a href="http://new.pmean.com/'
moved3 <- '<p>This page is moving to a <a href="http://new.pmean.com/'
moved4 <- '/">new website</a>.</p>'
moved2 <- '/">a new website</a>.</p>'
full_file_name <- paste0(old_path, html_files$yr, "/", html_files$fn)
html_links <- NULL
for (i_fn in full_file_name) {
  read_lines(i_fn) %>%
    str_subset(glue("({moved1}|{moved3})")) %>%
    str_replace(fixed(moved1), "") %>%
    str_replace(fixed(moved2), "") %>%
    str_replace(fixed(moved3), "") %>%
    str_replace(fixed(moved4), "") -> html_link
  html_link <- ifelse(length(html_link>0), html_link[1], "No link")
  html_file <- str_replace(i_fn, old_path, "")
  html_year <- str_sub(html_file, 1, 2)
  html_file <- str_sub(html_file, 4)
  html_links <- bind_rows(html_links, data.frame(html_year, html_file, html_link))
}
kable(html_links[1:10, ])
html_links %>%
  mutate(link=(html_link!="No link")) %>%
  count(html_year, link) %>%
  data.frame
```

>>>>

```{r md_links}
sim1 <- "[sim1]: http://www.pmean.com/"
full_file_name <- paste0(new_path, md_files$yr, "/", md_files$fn)
md_links <- NULL
for (i_fn in full_file_name) {
  read_lines(i_fn) %>%
    str_subset(fixed(sim1)) %>%
    str_replace(fixed(sim1), "") -> md_link
  md_link <- ifelse(length(md_link>0), md_link[1], "No link")
  md_file <- str_replace(i_fn, new_path, "")
  md_year <- str_sub(md_file, 1, 2)
  md_file <- str_sub(md_file, 4)
  md_links <- bind_rows(md_links, data.frame(md_year, md_file, md_link))
}
kable(md_links[1:10, ])
```

```{r md_year_summary}
md_links %>%
  mutate(link=(md_link!="No link")) %>%
  count(md_year, link) %>%
  pivot_wider(
    id_cols=md_year, 
    names_from=link, 
    names_prefix="linked_", 
    values_from=n,
    values_fill=0) %>%
  mutate(total=linked_FALSE+linked_TRUE) %>%
  data.frame -> yr_count
yr_count %>%
  summarize(
    linked_FALSE=sum(linked_FALSE),
    linked_TRUE=sum(linked_TRUE),
    total=sum(total)) %>%
  mutate(md_year="All") %>%
  bind_rows(yr_count, .)
```

@@

```{r html_links}
moved1 <- '<p>This page has moved to <a href="http://new.pmean.com/'
moved3 <- '<p>This page is moving to a <a href="http://new.pmean.com/'
moved4 <- '/">new website</a>.</p>'
moved2 <- '/">a new website</a>.</p>'
full_file_name <- paste0(old_path, html_files$yr, "/", html_files$fn)
html_links <- NULL
for (i_fn in full_file_name) {
  read_lines(i_fn) %>%
    str_subset(glue("({moved1}|{moved3})")) %>%
    str_replace(fixed(moved1), "") %>%
    str_replace(fixed(moved2), "") %>%
    str_replace(fixed(moved3), "") %>%
    str_replace(fixed(moved4), "") -> html_link
  html_link <- ifelse(length(html_link>0), html_link[1], "No link")
  html_file <- str_replace(i_fn, old_path, "")
  html_year <- str_sub(html_file, 1, 2)
  html_file <- str_sub(html_file, 4)
  html_links <- bind_rows(html_links, data.frame(html_year, html_file, html_link))
}
kable(html_links[1:10, ])
html_links %>%
  mutate(link=(html_link!="No link")) %>%
  count(html_year, link) %>%
  pivot_wider(
    id_cols=html_year, 
    names_from=link, 
    names_prefix="linked_", 
    values_from=n,
    values_fill=0) %>%
  mutate(total=linked_FALSE+linked_TRUE) %>%
  data.frame -> yr_count
yr_count %>%
  summarize(
    linked_FALSE=sum(linked_FALSE),
    linked_TRUE=sum(linked_TRUE),
    total=sum(total)) %>%
  mutate(html_year="All") %>%
  bind_rows(yr_count, .)
```
